New lower bounds for Schur and weak Schur numbers

### 2021-09-22 article/introduction.tex
fix refs + precisions

\par
In \hyperref[Schur]{Section 2}, we explain Rowley's template-based construction in the context of 
Schur numbers. Then, we give new templates, thus providing new lowers bounds and inequalities as well as 
showing that the growth rates for both Schur and Ramsey numbers \(R_n(3)\) exceed 3.28.

\par
In \hyperref[WeakSchur]{Section 3}, we generalize the concept of templates to weak Schur numbers 
and provide new lower bounds for weak Schur numbers.

>>>>

\par
In Section \ref{Schur}, we explain Rowley's template-based construction in the context of 
Schur numbers. Then, we give new templates, thus providing new lowers bounds and inequalities as well as 
showing that the growth rates for both Schur and Ramsey numbers \(R_n(3)\) exceed 3.28.

\par
In Section \ref{WeakSchur}, we generalize the concept of templates to weak Schur numbers 
and provide new lower bounds for weak Schur numbers. We then use a different approach and give a new 
lower bound for \(\WS(6)\).

### 2021-09-22 article/schur.tex
fix refs + precisions

\begin{theorem}
\label{Theorem2.4}
	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(S\)-template with width \(q\) and \(n+1\) colors 
	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there exists a partition of \([\![1,pq+m_{n+1}
	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
\end{theorem}

@@

\begin{corollary}
\label{Corollary2.5}
	Let \(n, k \in \mathbb{N}^*\). Then
	\[ S(n+k) \geqslant S^+(n+1)S(k) + m_{n+1} - 1 \]
\end{corollary}

@@

We now proceed to prove \hyperref[Theorem2.4]{Theorem 2.4}

@@

The following proposition may improve the additive constant of \hyperref[Corollary2.5]{Corollary 2.5}.

\begin{proposition}
\label{Proposition2.6}
Let \((q, n) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a S-template with width \(q\) and \(n+1\) 
colors. Let \(b \in \mathbb{N}\) and assume there is a coloring \(g\) of 
\([\![1, b]\!]\) with \(n+1\) colors such that:

@@

\begin{proof}[\textsc{Proof.}]
The idea is the same as in the \hyperref[Theorem2.4]{Theorem 2.4}. The only difference is the S-template property inherited 
from the second S-template. \\
\end{proof}

\subsection{New lower bounds for Schur numbers}
\label{Subsection2.3}
We now give the inequalities corresponding to the current  best S-templates (to our knowledge).

@@

\par
Here are the inequalities given by the current best S-templates (to our knowledge). The \hyperref[S-templates]{templates} 
corresponding to the third, fourth and fifth inequalities can be found in the appendix.

@@

\begin{proof}[\textsc{Proof.}]
It is a mere consequence of the inequality \( S(n+5) \geqslant 380S(n) + 148\). As for Ramsey
numbers, the following inequality holds \(S(n) \leqslant R_n(3) - 2\) (see \cite{AbbottHanson}) hence the result. \\
\end{proof}

>>>>

\begin{theorem}
\label{thm:Stemp}
	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(S\)-template with width \(q\) and \(n+1\) colors 
	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there exists a partition of \([\![1,pq+m_{n+1}
	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
\end{theorem}

@@

\begin{corollary}
\label{cor:ineqS}
	Let \(n, k \in \mathbb{N}^*\). Then
	\[ S(n+k) \geqslant S^+(n+1)S(k) + m_{n+1} - 1 \]
\end{corollary}

@@

We now proceed to prove Theorem \ref{thm:Stemp}.

@@

The following proposition may improve the additive constant of Corollary \ref{cor:ineqS}.

\begin{proposition}
\label{prop:rafStemp}
Let \((q, n) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a S-template with width \(q\) and \(n+1\) 
colors. Let \(b \in \mathbb{N}\) and assume there is a coloring \(g\) of 
\([\![1, b]\!]\) with \(n+1\) colors such that:

@@

\begin{proof}[\textsc{Proof.}]
The idea is the same as in the Theorem \ref{thm:Stemp}. The only difference is the S-template property inherited 
from the second S-template. \\
\end{proof}

\subsection{New lower bounds for Schur numbers}
\label{subsec:lowS}
We now give the inequalities corresponding to the current  best S-templates.

@@

\par
Here are the inequalities given by the current best S-templates. The \hyperref[S-templates]{templates} 
corresponding to the third, fourth and fifth inequalities can be found in the appendix.

@@

\begin{proof}[\textsc{Proof.}]
It is a mere consequence of the inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). As for Ramsey
numbers, the following inequality holds \(S(n) \leqslant R_n(3) - 2\) (see \cite{AbbottHanson}) hence the result. \\
\end{proof}
